### 2021-01-20 introduction.tex
integrating Handrick updates

Previous research studies have investigated the effectiveness of mining sandboxes, using automated testing tools, to compare the performance of each tool to mine sandboxes. For instance, Bao et al. \cite{bao2018mining} present the results of an empirical study comparing 5 automated testing tools: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}. The study measured the efficiency of each tool, as well as if the combination of one or more of them could lead to performance improvements. That research work consisted of performing experiments in pairs of apps, one benign and one malign that piggybacks the corresponding benign app, leading to malicious behavior. The dataset used comprised of 102 pairs of benign and malign apps (B/M). This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in this dataset and also reports that, after combining 5 test generator tools, it was possible to detect 80\% of malicious behavior. Nonetheless, the field of automatic test generation of mobile apps is everything but listless---many promising automatic test generation tools have been recently proposed
~\cite{cai2020longitudinal,li2019deep}, which might outperform previous tools that have been used to mine sandboxes.

@@

In this paper, we further dig into the role of static analysis order for malware detecting. Specifically, we aim at understanding how static analysis might be useful and help dynamic analysis in the process of mining android sandboxes. To this end, we conducted a non-exact replication of the study of Bao et al, supported by a benchmark solution, called DroidXP \cite{dadroidxp}, whose main objective is  assist researchers and practitioners to integrate test case generation tools and compare their performance on mining android sandboxes. Our study differs from the original in the following aspects. First, we refined the dataset used, analyzing 96 pairs of apps (B/M). Second, we introduced in our study, two recent tools that were not considered in the previous work. Finally, we evaluate the role of each kind of analysis, static and dynamic, regarding the performance of the analyzed tools.

@@

We organize the remainder of this paper as follows. Section 2 describes all the apps malware used in our experiment, presenting their characterization. Section 3 introduces the benchmark solution used to replicate the study presented in this paper. Section 4 describes the original experiment, its replication, and its results as well. Section 5 highlights some motivation malware example, discovered in our research, and its attack strategy. In section 6 we present the use of a promising static analysis tool, in our motivation example. Finally, Sections 7 and 8, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

>>>>

Previous research studies have investigated the effectiveness of mining sandboxes, using automated testing tools, to compare the performance of each tool to mine sandboxes. For instance, Bao et al. \cite{bao2018mining} present the results of an empirical study comparing 5 automated testing tools: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}. The study measured the efficiency of each tool, as well as if the combination of one or more of them could lead to performance improvements. That research work consisted of performing experiments in pairs of apps, one benign and one malign (B/M), that piggybacks the corresponding benign app, leading to malicious behavior. This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, after combining 5 test generator tools, it was possible to detect 80\% of malicious behavior. Nonetheless, the field of automatic test generation of mobile apps is everything but listless---many promising automatic test generation tools have been recently proposed
~\cite{cai2020longitudinal,li2019deep}, which might outperform previous tools that have been used to mine sandboxes.

@@

In this paper, we further dig into the role of static analysis order for malware detecting. Specifically, we aim at understanding how static analysis might be useful and help dynamic analysis in the process of mining android sandboxes. To this end, we conducted a non-exact replication of the study of Bao et al, supported by a benchmark solution, called droidXP \cite{dadroidxp}, whose main objective is  assist researchers and practitioners to integrate test case generation tools and compare their performance on mining android sandboxes. Our study differs from the original in the following aspects. First, we refined the dataset used, and executed the analysis of each apps, for a time biggest than the original experiment. Second, we introduced in our study, two tools that were not considered in the previous work. Finally, we evaluate the role of each kind of analysis, static and dynamic, regarding the performance of the analyzed tools.

@@

We organize the remainder of this paper as follows. Section 2 describes all the apps malware used in our experiment, presenting their characterization. Section 3 introduces the study setting of our research. Section 4 describes the benchmark solution used in our experiment. Section 5 presented some results, highlighting some motivation malware example, which will be described at Section 6. Section 7 we present the use of a promising static analysis tool, in our motivation example. Finally, Sections 7 and 8, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

### 2021-01-20 setup.tex
Just a review of the study settings organization.
integrating Handrick updates

\section{Experimental Setup}
\begin{figure*}[h!]
  \includegraphics[width=0.5\textwidth]{images/setup.png}
  \label{Experiment setup}
  \caption{Experiment setup}
  \label{fig:setup}
\end{figure*}

To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox. Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app. (Figure  \ref{fig:setup}) show all the experimental setup.

>>>>

\section{Study Settings}

Before the conception of droidXP, there were studies that provided valuable information about the comparison between test generation tools \cite{bao2018mining}\cite{hao2014puma}. This data was required to measure the benchmark droidXP's performance and precision. Particularly, L Bao et al. \cite{bao2018mining} had provided an important comparative study between five test generation tools in finding malware using mining sandboxes techniques, and that inspired our study settings. His first experiment used a small set of apps (10 pairs B/M) to be run for different periods of time to compare how much time the tools needed to achieve the maximum coverage possible and to identify the sensitive APIs accessed. This study showed that the coverage and accuracy of the testing tool have a negative correlation. That is, improving the performance of code coverage might not directly contribute to the performance of detecting malware. The second experiment used a set of 102 pairs of apps that were executed for just one minute. The goal of this experiment was to compare a bigger number of apps and the number of sensitive APIs accessed by each tool in a small time. However, this study did not focus on the possible interference of the DroidFax \cite{cai2017droidfax} tool on the benchmark results. The benchmark uses DroidFax to analyze Android apps during execution, but this tool also performs a static analysis of the apps.

The first empirical study had shown useful aspects of the tools while being executed by the benchmark droidXP. To replicate the previous studies, we choice a subset of pairs (B/M), based on the set of pairs presented by L Bao et al. The addition of Humanoid and the fake tools, "Joke", in the comparison brought newer techniques that explored Android apps better.

Hence, the main goal of this research work is
to understand the influence of the static analysis, which is performed by DroidFax, in the benchmark execution. To achieve this general goal, we answer the following research questions.

\begin{enumerate}[(RQ1)]
\item What is the effective performance of each tool in terms of the number of detected malware ?
\item What benefits of using a hybrid approach, which combines static and dynamic analysis, for mining sandboxes ?
\item What is the impact of DroidFax’s static analysis on benchmark results ?
\end{enumerate}

In the first experiment, we executed the benchmark considering 98 pairs of apps for 3 minutes. At this time, we used a new option of the benchmark that disables the static analysis performed by DroidFax. So, we used this experiment to answer the first research questions (RQ1). In the second experiment, we executed all apps with a fake tool called “Joke”, which does not do anything during the benchmark execution, to compute the results without the dynamic analysis influence. With these results, we can answer the last two research question (RQ2 and RQ3).

\subsection{Settings for RQ1}

To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox. Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app. (Figure  \ref{fig:setup}) show all this experimental setup.

\subsection{Settings for RQ2 and RQ3}

\begin{figure*}[h!]
  \includegraphics[width=0.5\textwidth]{images/setup.png}
  \label{Experiment setup}
  \caption{Experiment setup}
  \label{fig:setup}
\end{figure*}
